Multilevel selection in causal models: the non-ergodicity of evolutionary and probability theories as the general driver of the emergence of cooperation and specialization.

### 2022-02-28 article.tex
doc.1.0.1

%opening
\title{\vspace{-2.2cm}Multilevel selection in causal models: the multiplicative nature of evolutionary and probabilistic selection processes as the general driver for the irreversibility emergence of cooperation and specialization.\footnote{\url{https://github.com/glandfried/transitions/releases/download/doc1.0.0/landfried-transitions.pdf}} }
\author{Gustavo Landfried$^1$}
\affil{\small 1. Universidad de Buenos Aires. Facultad de Ciencias Exactas y Naturales. Departamento de Computaci\'on. Buenos Aires, Argentina}
\affil{\en{Mail}\es{Correo:} \url{glandfried@dc.uba.ar}}

@@

\lim_{T \rightarrow \infty} f(\text{cara})^{n_1/T} f(\text{seca})^{n_2/T} & 

>>>>

%opening
\title{\vspace{-2.2cm}Multilevel selection in causal models: the multiplicative nature of evolutionary and probabilistic selection processes as the general driver for the irreversibility emergence of cooperation and specialization.\footnote{\url{https://github.com/glandfried/transitions/releases/download/doc1.0.1/landfried-\en{transitions}\es{transiciones}.pdf}} }
\author{Gustavo Landfried$^1$}
\affil{\small 1. Universidad de Buenos Aires. Facultad de Ciencias Exactas y Naturales. Departamento de Computaci\'on. Buenos Aires, Argentina}
\affil{\en{Mail}\es{Correo:} \url{glandfried@dc.uba.ar}}

@@

\lim_{T \rightarrow \infty} f(\text{\en{head}\es{cara}})^{n_1/T} f(\text{\en{tail}\es{seca}})^{n_2/T} & 
